Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Remove stray todo
Tweak intro

There have been several attempts to standardise and deploy new transport 
protocols \cite{rfc:4340,RFC4960}.
In practice, however, only UDP and TCP are widely usable in the Internet,
since the remaining protocols are blocked by firewalls and other
middleboxes. UDP exposes the best-effort IP packet delivery service,
offering the flexibility to develop new protocols, but at the cost of
requiring new mechanisms to be defined and implemented from scratch.
In contrast, TCP mechanisms are well defined, consisting of sophisticated
congestion control coupled with a reliable, ordered, byte stream API.
These are proven suitable for many applications, but are inappropriate
for real-time traffic. While both protocols may be used for real-time
applications, neither really provides the right services and API. This
forces each application to re-invent or re-interpret mechanisms that
should be provided by the transport. The increased costs and
complexity of doing so raise barriers to innovation.

@@

\todo{Review A: Section 4 should have a forward reference to section 5}
%==================================================================================================
\section{Realising Transport Services}
\label{sec:realising}

>>>>

There have been several attempts to standardise and deploy new transport 
protocols \cite{rfc:4340,RFC4960}.
In practice, however, only UDP and TCP are widely usable in the Internet,
since the remaining protocols are blocked by firewalls and other
middleboxes. UDP exposes the best-effort IP packet delivery service,
offering the flexibility to develop new protocols, but at the cost of
requiring new mechanisms to be defined and implemented from scratch.
In contrast, TCP mechanisms are well defined, consisting of sophisticated
congestion control coupled with a reliable, ordered, byte stream API.
These have been proven suitable for many applications, but are inappropriate
for real-time traffic. While both protocols are used for real-time
applications, neither really provides the right services and API. This
forces each application to re-invent or re-interpret mechanisms that
should be provided by the transport. The increased costs and
complexity of doing so make applications less reliable, and raise barriers to innovation.

@@

%==================================================================================================
\section{Realising Transport Services}
\label{sec:realising}
